---
title: "Introduction to covid19usa R package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to covid19usa R package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(covid19usa)
library(dplyr)
library(tibble)
```

# Getting Started: Launching the App

The Shiny web application can be launched with a single line of code:

```{r launch-app, eval = FALSE}
launch_app()
```

# What the App Does

## The Datasets

The package retrieves Covid-19 datasets from [The New York Times](https://github.com/nytimes/covid-19-data)) and [Covidtracking.com](https://covidtracking.com/data). These datasets are combined with the U.S map data to provide an interactive map and other data visualisations to allow users to explore Covid-19 cases across the U.S. Several interactive features are included to allow for a more personalised information with the ability to manoeuvre between dates and states across U.S.

The datasets can be retrieved with theses functions embedded in the package:

```{r}
covid_us_states %>% tibble() 

tests_raw %>% tibble()

us_pop_ests %>% tibble()

us_states_map %>% tibble()
```

The combined spatial datasets can be retrieved with these functions:

```{r}
create_map_data()
```

# What the App Does

The Shiny App consists of two main tabs:

### Tab 1: Comparing Confirmed Covid-19 Cases (per 100,000 Population) across U.S States


![please](tab1_example.mp4)

<video width="320" height="240" controls>
  <source src="tab1_example.mp4" type="video/mp4">
</video>

### Tab 2: Positive Covid-19 Cases found via Covid-19 Testing
